---
title: "Zero Determinant Strategies and their Transfer entropy"
output: html_notebook
---

This is a notebook to document my attempts to develop a zero determinant strategy in R, play it against other strategies, and examine the transfer entropy over time.  Dyson & .... provide the mathematical underpinnings for this code, and python script at https://github.com/CamDavidsonPilon/ipd/blob/master/ipd.py
has a simple script for ZD strategies.  I will use both to generate my own script below


```{r}
zd <- read.csv("/Users/Home1/Desktop/Classes/Spring_2018/Complex_adaptive_systems/CAS_code/Complex_adaptive_systems/Assignment3/a3_df.csv")

zd$X <- NULL

zd$p1state <- ifelse(zd$Score1 == 3 & zd$Score2 == 3, "COOPERATE", NA)
zd$p2state <- ifelse(zd$Score1 == 3 & zd$Score2 == 3, "COOPERATE", NA)

zd$p1state <- ifelse(zd$Score1 == 0 & zd$Score2 == 5, "COOPERATE", zd$p1state)
zd$p2state <- ifelse(zd$Score1 == 0 & zd$Score2 == 5, "DEFECT", zd$p2state)

zd$p1state <- ifelse(zd$Score1 == 5 & zd$Score2 == 0, "DEFECT", zd$p1state)
zd$p2state <- ifelse(zd$Score1 == 5 & zd$Score2 == 0, "COOPERATE", zd$p2state)

zd$p1state <- ifelse(zd$Score1 == 1 & zd$Score2 == 1, "DEFECT", zd$p1state)
zd$p2state <- ifelse(zd$Score1 == 1 & zd$Score2 == 1, "DEFECT", zd$p2state)

zd$p1statenum <- ifelse(zd$p1state == "COOPERATE", 1, 0)
zd$p2statenum <- ifelse(zd$p2state == "COOPERATE", 1, 0)


#### Split by strategy and extortion value, then calculate transfer entropy between Score1 and Score 2

```

Setting up the jidt tool using the provided example script
```{r}
##
##  Java Information Dynamics Toolkit (JIDT)
##  Copyright (C) 2012, Joseph T. Lizier
##  
##  This program is free software: you can redistribute it and/or modify
##  it under the terms of the GNU General Public License as published by
##  the Free Software Foundation, either version 3 of the License, or
##  (at your option) any later version.
##  
##  This program is distributed in the hope that it will be useful,
##  but WITHOUT ANY WARRANTY; without even the implied warranty of
##  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
##  GNU General Public License for more details.
##  
##  You should have received a copy of the GNU General Public License
##  along with this program.  If not, see <http://www.gnu.org/licenses/>.
##
dyn.load(paste0(system2('/usr/libexec/java_home', stdout = TRUE), '/lib/server/libjvm.dylib'))
library(rJava)
library(dplyr)

setwd('/Users/Home1/Desktop/Classes/Spring_2018/Complex_adaptive_systems/infodynamics-dist-1.4')
.jinit(".")
.jaddClassPath("/Users/Home1/Desktop/Classes/Spring_2018/Complex_adaptive_systems/infodynamics-dist-1.4/infodynamics.jar")
strat.list <- list()
system.time(
for (ii in unique(zd$P2strategy)){

zd2 <- subset(zd, P2strategy == ii)
extort.list <- list()
for (i in seq(from = 1, to = 13, by = 0.1)){
# Create a TE calculator and run it:
teCalc<-.jnew("infodynamics/measures/discrete/TransferEntropyCalculatorDiscrete",
              2L,
              1L)
.jcall(teCalc,
       "V",
       "initialise") # V for void return value
.jcall(teCalc,
       "V",
       "addObservations",
       as.integer(subset(zd2, Extortion == i)$p1statenum),
       as.integer(subset(zd2, Extortion == i)$p2statenum))

result1 <- .jcall(teCalc,
                  "D",
                  "computeAverageLocalOfObservations")

teCalc<-.jnew("infodynamics/measures/discrete/TransferEntropyCalculatorDiscrete",
              2L,
              1L)
.jcall(teCalc,
       "V",
       "initialise") # V for void return value
.jcall(teCalc,
       "V",
       "addObservations",
       as.integer(subset(zd2, Extortion == i)$p2statenum),
       as.integer(subset(zd2, Extortion == i)$p1statenum))

result2 <- .jcall(teCalc,"D","computeAverageLocalOfObservations")
extort.list[[as.character(i)]] <- data.frame(result1, result2, "Extortion" = i)
}

df1 <- do.call(rbind, extort.list)
df1 <- data.frame(df1, "Strategy" = ii)
strat.list[[ii]] <- df1
}
)
strat.df <- do.call(rbind, strat.list)


```

  
Analysis of python generated code

```{r}
library(ggplot2)
ggplot(strat.df) + geom_line(aes(Extortion, result1, color = Strategy)) + geom_line(aes(Extortion, result2, color =Strategy), linetype = "dashed")

ggplot(zd) + geom_line(aes(Matchnumber, Meanscore1, color = Extortion)) + facet_wrap(~P2strategy)

ggplot(zd) + geom_line(aes(Matchnumber, Score1, color = Extortion)) + facet_wrap(~P2strategy)

ggplot(strat.df) + geom_histogram(aes(result1))
ggplot(strat.df) + geom_histogram(aes(result2))


```

Below are some independent ones based on existing scripts:



```{r}
opposite_move <- function(move){
    if (move == "DEFECT"){
        return("COOPERATE")
        }
    if (move == "COOPERATE"){
        return("DEFECT")
        }
}

score <- function(my_move, opponents_move){
    if(my_move == "DEFECT" & opponents_move == "DEFECT" & !is.na(my_move == "DEFECT" & opponents_move == "DEFECT" )){
        return(1)}
    if(my_move == "COOPERATE" & opponents_move == "DEFECT" & !is.na(my_move == "COOPERATE" & opponents_move == "DEFECT")){
        return(0)}
    if(my_move == "DEFECT" & opponents_move == "COOPERATE" & !is.na(my_move == "DEFECT" & opponents_move == "COOPERATE" )){
        return(5)}
    if(my_move == "COOPERATE" & opponents_move == "COOPERATE" & !is.na(my_move == "COOPERATE" & opponents_move == "COOPERATE")){
        return(3)}
}




IPD <- function(p1, p2, n_matches = 10, extort_factor){

zd <- data.frame("t" = 0:n_matches, "move1" = NA, "move2" = NA, "score1" = NA, "score2" = NA, "meanscore1" = NA, "meanscore2" = NA, "scoresum1" = NA,"scoresum2" = NA)
zd[zd$t == 0, "score1"] <- 0
zd[zd$t == 0, "score2"] <- 0
zd[zd$t == 0, "move2"] <- "COOPERATE"
 zd[zd$t == 0, "move1"] <- "COOPERATE"
 
for (i in 1:n_matches){
### Pavlov
if (p1 == "Pavlov"){

      

      zd[zd$t == i, "move1"] <-ifelse(zd[zd$t == i - 1, "score1"] <= 1,
      	 opposite_move(zd[zd$t == i - 1, "move1"]),
      	 zd[zd$t == i - 1, "move1"])



}
if (p2 == "Pavlov"){

       

      zd[zd$t == i, "move2"] <-ifelse(zd[zd$t == i -1, "score2"] <= 1,
      	 opposite_move(zd[zd$t == i - 1, "move2"]),
      	 zd[zd$t == i - 1, "move2"])

}


###TFT    
if (p1 == "TFT"){

       zd[zd$t == 0, "move1"] <- "COOPERATE"
            
      zd[zd$t == i, "move1"] <-  zd[zd$t == i - 1, "move2"]

}

if (p2 == "TFT"){

       zd[zd$t == 0, "move2"] <- "COOPERATE"
            
      zd[zd$t == i, "move2"] <- zd[zd$t == i - 1, "move1"]

}

####Random

if (p2 == "Random"){

       zd[zd$t == 0, "move2"] <- sample(c("COOPERATE","DEFECT"), 1)
     
      zd[zd$t == i, "move2"] <- sample(c("COOPERATE","DEFECT"), 1)

}

if (p1 == "Random"){

       zd[zd$t == 0, "move1"] <- sample(c("COOPERATE","DEFECT"), 1)
           
      zd[zd$t == i, "move1"] <- sample(c("COOPERATE","DEFECT"), 1)

}

####Always Defect
if (p1 == "AD"){
      zd[zd$t == 0, "move1"] <- "DEFECT" 

      zd[zd$t == i, "move1"] <- "DEFECT"

}

if (p2 == "AD"){
      zd[zd$t == 0, "move2"] <- "DEFECT"

      zd[zd$t == i, "move2"] <- "DEFECT"

}

####Always Cooperate
if (p1 == "AC"){
      zd[zd$t == 0, "move1"] <- "COOPERATE" 

      zd[zd$t == i, "move1"] <- "COOPERATE"


}
if (p2 == "AC"){
       zd[zd$t == 0, "move2"] <- "COOPERATE"      

      zd[zd$t == i, "move2"] <- "COOPERATE"


}


#### Extortion
if (p1 == "Extortion"){
       zd[zd$t == 0, "move1"] <- "COOPERATE"

      	if(zd[zd$t == (i - 1) , "move1"] == "COOPERATE" & zd[zd$t == (i - 1) , "move2"] == "COOPERATE" & !is.na(zd[zd$t == i - 1 , "move1"] == "COOPERATE" & zd[zd$t == i - 1 , "move2"] == "COOPERATE")){
      		zd[zd$t == i , "move1"] <- ifelse(runif(1) < (1 - (2 * extort_factor - 2.) / (4. * extort_factor + 1.)), "COOPERATE", "DEFECT")
      		}
      		
      	if(zd[zd$t == (i - 1) , "move1"] == "DEFECT" & zd[zd$t == (i - 1) , "move2"] == "DEFECT" & !is.na(zd[zd$t == i - 1 , "move1"] == "DEFECT" & zd[zd$t == i - 1 , "move2"] == "DEFECT")){
      		zd[zd$t == i , "move1"] <-  "DEFECT"
      		}
      	
      	if(zd[zd$t == i - 1 , "move1"] == "COOPERATE" & zd[zd$t == i - 1 , "move2"] == "DEFECT" & !is.na(zd[zd$t == i - 1 , "move1"] == "COOPERATE" & zd[zd$t == i - 1 , "move2"] == "DEFECT")){
      		zd[zd$t == i , "move1"] <-  "DEFECT"
      		}
      		
      	if(zd[zd$t == i - 1 , "move1"] == "DEFECT" & zd[zd$t == i - 1 , "move2"] == "COOPERATE" & !is.na(zd[zd$t == i - 1 , "move1"] == "DEFECT" & zd[zd$t == i - 1 , "move2"] == "COOPERATE")){
      		zd[zd$t == i , "move1"] <- ifelse(runif(1) < ((extort_factor + 4) / (4. * extort_factor + 1)), "COOPERATE", "DEFECT")
      		}	

}

if (p2 == "Extortion"){   
      	 zd[zd$t == 0, "move2"] <- "COOPERATE"

      	if(zd[zd$t == i - 1 , "move2"] == "COOPERATE" & zd[zd$t == i - 1 , "move1"] == "COOPERATE" & !is.na(zd[zd$t == i - 1 , "move2"] == "COOPERATE" & zd[zd$t == i - 1 , "move1"] == "COOPERATE")){
      		zd[zd$t == i , "move2"] <- ifelse(runif(1) < (1 - (2 * extort_factor - 2.) / (4. * extort_factor + 1.)), "COOPERATE", "DEFECT")
      		}
      		
      	if(zd[zd$t == i - 1 , "move2"] == "DEFECT" & zd[zd$t == i - 1 , "move1"] == "DEFECT" & !is.na(zd[zd$t == i - 1 , "move2"] == "DEFECT" & zd[zd$t == i - 1 , "move1"] == "DEFECT")){
      		zd[zd$t == i , "move2"] <-  "DEFECT"
      		}
      		      	if(zd[zd$t == i - 1 , "move2"] == "COOPERATE" & zd[zd$t == i - 1 , "move1"] == "DEFECT" & !is.na(zd[zd$t == i - 1 , "move2"] == "COOPERATE" & zd[zd$t == i - 1 , "move1"] == "DEFECT")){
      		zd[zd$t == i , "move2"] <-  "DEFECT"
      		}
      		
      	if(zd[zd$t == i - 1 , "move2"] == "DEFECT" & zd[zd$t == i - 1 , "move1"] == "COOPERATE" & !is.na(zd[zd$t == i - 1 , "move2"] == "DEFECT" & zd[zd$t == i - 1 , "move1"] == "COOPERATE")){
      		zd[zd$t == i , "move2"] <- ifelse(runif(1) < ((extort_factor + 4) / (4. * extort_factor + 1)), "COOPERATE", "DEFECT")
      		}	

}

##### go by majority, memory == 20

if (p1 == "gobymajority"){
	zd[zd$t == 0, "move1"] <- "COOPERATE"      
    zd[zd$t == i, "move1"] <- ifelse(sum(zd[c(ifelse(i-20 < 0, 0, (i-20)):i),"move2"] == "COOPERATE", na.rm = T) >= sum(zd[c(ifelse(i-20 < 0, 0, (i-20)):i),"move2"] == "DEFECT", na.rm = T), "COOPERATE", "DEFECT")
    }

if (p2 == "gobymajority"){
	zd[zd$t == 0, "move2"] <- "COOPERATE"      
    zd[zd$t == i, "move2"] <- ifelse(sum(zd[c(ifelse(i-20 < 0, 0, (i-20)):i),"move1"] == "COOPERATE", na.rm = T) >= sum(zd[c(ifelse(i-20 < 0, 0, (i-20)):i),"move1"] == "DEFECT", na.rm = T), "COOPERATE", "DEFECT")
    }

#### my majority vs their majority
if (p1 == "majorityvsmajority"){
	zd[zd$t == 0, "move1"] <- "COOPERATE"      
    zd[zd$t == i, "move1"] <- ifelse(sum(zd[c(ifelse(i-20 < 0, 0, (i-20)):i),"move1"] == "COOPERATE", na.rm = T) > sum(zd[c(ifelse(i-20 < 0, 0, (i-20)):i),"move2"] == "COOPERATE", na.rm = T), "DEFECT", "COOPERATE")
    }

if (p2 == "majorityvsmajority"){
	zd[zd$t == 0, "move2"] <- "COOPERATE"      
  zd[zd$t == i, "move2"] <- ifelse(sum(zd[c(ifelse(i-20 < 0, 0, (i-20)):i),"move2"] == "COOPERATE", na.rm = T) > sum(zd[c(ifelse(i-20 < 0, 0, (i-20)):i),"move1"] == "COOPERATE", na.rm = T), "DEFECT", "COOPERATE")
    }

#### my majority vs their majority, random
if (p1 == "majorityvsmajorityrandom"){
	zd[zd$t == 0, "move1"] <- "COOPERATE"      
    zd[zd$t == i, "move1"] <- ifelse(sum(zd[c(ifelse(i-20 < 0, 0, (i-20)):i),"move1"] == "COOPERATE", na.rm = T) > sum(zd[c(ifelse(i-20 < 0, 0, (i-20)):i),"move2"] == "COOPERATE", na.rm = T), sample(c("DEFECT", "COOPERATE"), 1), "COOPERATE")
    }

if (p2 == "majorityvsmajorityrandom"){
	zd[zd$t == 0, "move2"] <- "COOPERATE"      
  zd[zd$t == i, "move2"] <- ifelse(sum(zd[c(ifelse(i-20 < 0, 0, (i-20)):i),"move2"] == "COOPERATE", na.rm = T) > sum(zd[c(ifelse(i-20 < 0, 0, (i-20)):i),"move1"] == "COOPERATE", na.rm = T), sample(c("DEFECT", "COOPERATE"), 1), "COOPERATE")
    }

##### Grudger

if (p1 == "grudger"){
	zd[zd$t == 0,"move1"] <- "COOPERATE"
	zd[zd$t == i,"move1"] <- ifelse(sum(zd[c(ifelse(i-10 < 0, 0, (i-10)):i),"move2"] == "DEFECT", na.rm = T) > 1, "DEFECT", "COOPERATE")
    }

if (p2 == "grudger"){
	zd[zd$t == 0,"move2"] <- "COOPERATE"
	zd[zd$t == i,"move2"] <- ifelse(sum(zd[c(ifelse(i-10 < 0, 0, (i-10)):i),"move1"] == "DEFECT", na.rm = T) > 1, "DEFECT", "COOPERATE")
    }


  #### Mindreader
if (p2 == "mindreader"){
zd1 <- subset(zd, t < i & t > i - 20)
zd1$move1 <- ifelse(zd1$move1 == "COOPERATE", 1, 0)
zd1$move2 <- ifelse(zd1$move2 == "COOPERATE", 1, 0)

zd.glm <- glm(move1 ~ move2, data = zd1, family = binomial())

z.d2 <- data.frame("move2" = sample(c(0,1), 100, replace = T), "punish" = NA)
z.d2$move1 <- predict.glm(zd.glm, newdata = z.d2, "response")
z.d2$move1 <- ifelse(z.d2$move1 > 0.3, 1, 0)

#does player 2 punish player 1 for defection?

for (nn in 1:(nrow(z.d2)-1)){
z.d2[nn, "punish"] <- ifelse(z.d2[nn, "move2"] == 0 & z.d2[nn + 1,"move1"] != 0, 1, 0)
}
zd[zd$t == i, "move2"] <- ifelse(mean(z.d2$punish, na.rm = T) > 0.3, "DEFECT","COOPERATE")

}
  
#### scoring
zd[zd$t == i, "score1"] <- score(zd[zd$t == i, "move1"], zd[zd$t == i, "move2"])
zd[zd$t == i, "score2"] <- score(zd[zd$t == i, "move2"], zd[zd$t == i, "move1"])

zd[zd$t == i, "meanscore1"] <- mean(zd[,"score1"], na.rm = T)
zd[zd$t == i, "meanscore2"] <- mean(zd[,"score2"], na.rm = T)

zd[zd$t == i, "scoresum1"] <- sum(zd[,"score1"], na.rm = T)
zd[zd$t == i, "scoresum2"] <- sum(zd[,"score2"], na.rm = T)
}
return(zd)
}

```


and now running through every iteration




```{r}
options(warn=-1)
strategies <- c("Pavlov","TFT","AC","AD","Random","Extortion","gobymajority","majorityvsmajority","majorityvsmajorityrandom","grudger", "mindreader")
s.list <- list()
for (ss in strategies){
  zd.list <- list()
  for (ee in seq(from = 1, to = 13, by = 0.1)){
  df <- IPD(p1 ="Extortion", p2 = ss, extort_factor = ee, n_matches = 1000)
  df$extort_factor <- ee
  zd.list[[as.character(ee)]] <- df
  }
  df.s <- do.call(rbind, zd.list)
  df.s$strategy <- ss
  s.list[[ss]] <- df.s
}

df.strategies <- do.call(rbind, s.list)

df.strategies$p1statenum <- ifelse(df.strategies$move1 == "COOPERATE", 1, 0)
df.strategies$p2statenum <- ifelse(df.strategies$move2 == "COOPERATE", 1, 0)


##
##  Java Information Dynamics Toolkit (JIDT)
##  Copyright (C) 2012, Joseph T. Lizier
##  
##  This program is free software: you can redistribute it and/or modify
##  it under the terms of the GNU General Public License as published by
##  the Free Software Foundation, either version 3 of the License, or
##  (at your option) any later version.
##  
##  This program is distributed in the hope that it will be useful,
##  but WITHOUT ANY WARRANTY; without even the implied warranty of
##  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
##  GNU General Public License for more details.
##  
##  You should have received a copy of the GNU General Public License
##  along with this program.  If not, see <http://www.gnu.org/licenses/>.
##
dyn.load(paste0(system2('/usr/libexec/java_home', stdout = TRUE), '/lib/server/libjvm.dylib'))
library(rJava)
library(dplyr)

setwd('/Users/Home1/Desktop/Classes/Spring_2018/Complex_adaptive_systems/infodynamics-dist-1.4')
.jinit(".")
.jaddClassPath("/Users/Home1/Desktop/Classes/Spring_2018/Complex_adaptive_systems/infodynamics-dist-1.4/infodynamics.jar")
strat.list <- list()
system.time(
for (ii in unique(df.strategies$strategy)){

zd2 <- subset(df.strategies, strategy == ii)
extort.list <- list()
for (i in seq(from = 1, to = 13, by = 0.1)){
# Create a TE calculator and run it:
teCalc<-.jnew("infodynamics/measures/discrete/TransferEntropyCalculatorDiscrete",
              2L,
              1L)
.jcall(teCalc,
       "V",
       "initialise") # V for void return value
.jcall(teCalc,
       "V",
       "addObservations",
       as.integer(subset(zd2, extort_factor == i)$p1statenum),
       as.integer(subset(zd2, extort_factor == i)$p2statenum))

result1 <- .jcall(teCalc,
                  "D",
                  "computeAverageLocalOfObservations")

teCalc<-.jnew("infodynamics/measures/discrete/TransferEntropyCalculatorDiscrete",
              2L,
              1L)
.jcall(teCalc,
       "V",
       "initialise") # V for void return value
.jcall(teCalc,
       "V",
       "addObservations",
       as.integer(subset(zd2, extort_factor == i)$p2statenum),
       as.integer(subset(zd2, extort_factor == i)$p1statenum))

result2 <- .jcall(teCalc,"D","computeAverageLocalOfObservations")
extort.list[[as.character(i)]] <- data.frame(result1, result2, "Extortion" = i)
}

df1 <- do.call(rbind, extort.list)
df1 <- data.frame(df1, "Strategy" = ii)
strat.list[[ii]] <- df1
}
)
strat.df <- do.call(rbind, strat.list)

save(strat.df, file = "~/Desktop/strat_df3.rda")
save(df.strategies, file = "~/Desktop/df_strategies3.rda")

options(warn=0)
```


```{r}
library(ggplot2)
library(dplyr)
load("~/Desktop/strat_df3.rda")
load("~/Desktop/df_strategies3.rda")
ggplot(df.strategies) + geom_boxplot(aes(as.character(strategy),meanscore1),fill = "blue", outlier.shape = NA) + geom_boxplot(aes(as.character(strategy),meanscore2),fill = "red", outlier.shape = NA) + theme_bw() + scale_fill_manual(labels = c("Extortion", "Opponent"), values = c("blue","red")) + labs(x = "Strategy", y = "Mean Score (1000 steps)")+ theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggsave("~/Desktop/fig1CAS.jpg", h = 4, w = 3)

ggplot(strat.df) + geom_line(aes(Extortion, result1), color = "blue") + geom_line(aes(Extortion, result2), color = "red") + facet_wrap(~Strategy) + theme_bw() + labs(x = "Extortion Factor", y = "Transfer Entropy") + theme(legend.position="bottom")

ggsave("~/Desktop/fig2CAS.jpg", h = 4, w = 3)

ggplot(subset(df.strategies, t <= 100 & extort_factor == c(1, 3, 7, 10))) + geom_line(aes(t,score1, color = as.character(extort_factor))) + facet_wrap(~strategy) + theme_bw() + labs(x = "Time", y = "Score") + scale_color_brewer(palette = "Spectral", name = "Extort Factor") + theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="bottom")

ggsave("~/Desktop/fig3CAS.jpg", h = 4, w = 3)
shannonsH <- function(mystring){
  freqs <- mystring / sum(mystring, na.rm = T)
  H <- -sum(freqs * log(freqs) / log(2), na.rm = T)
  return(H)
}
df.strat.entrop <- df.strategies %>%
  group_by(extort_factor, strategy) %>%
  summarize("ShannonH1" = shannonsH(score1),
            "ShannonH2" = shannonsH(score2))

ggplot(df.strat.entrop) + geom_line(aes(extort_factor, ShannonH1), color = "blue") + geom_line(aes(extort_factor, ShannonH2), color = "red") + facet_wrap(~strategy) + theme_bw() +
  labs(x = "Extortion Factor", y = "Shannon's H") + theme(legend.position="bottom")
ggsave("~/Desktop/fig35CAS.jpg", h = 4, w = 3)

### how many possible values per strat as extortion factor increases?

df.strat.len <- subset(df.strategies, t > 100) %>%
  group_by(extort_factor, strategy) %>%
  summarize("r1" = length(unique(score1)),
            "r2" = length(unique(score2)))


ggplot(df.strat.len) + geom_line(aes(extort_factor, r1), color = "blue") + geom_line(aes(extort_factor, r2), color = "red") + facet_wrap(~strategy) + labs(x = "Extortion Factor", y = "Possible Scores") + theme_bw() + theme(legend.position="bottom")

ggsave("~/Desktop/fig4CAS.jpg", h = 4, w = 3)

```

